Supplemental Information:\\ Harnessing Design Principles from Glass Sponges for Structurally Robust Lattice Structures

### 2018-10-03 Supplemental-FernandesWeaverBertoldi_AdvMaterials_2018.tex
.

For all buckling analysis, we performed a linear stability buckling analysis ({\tt *Buckling} command in ABAQUS input file). We perform this analysis for varying angles $\theta$ and extract the first mode critical buckling strain. Since buckling may alter the periodicity of the
structure, we considered super cells consisting of $M \times M$
undeformed RVEs subjected to periodic boundary
conditions and calculated the critical strain for each of
them. The critical strain of the infinite periodic structure is
then defined as the minimum critical strain on all considered
super cells.

\KB{it would be good to add this plot for each Design. Similar to Fig. 2c in "Complex Ordered Patterns in Mechanical Instability Induced Geometrically
Frustrated Triangular Cellular Structures"} \mf{Yes, I like this plot and will work on creating it.}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{SFig6.png}
    \caption{{\bf Buckling Optimization.} Graph shows optimal value of critical buckling strain for varying number of diagonals. For all simulations, the total mass of the structure is maintained constant while the mass-ratio is allowed to vary. Furthermore, the diagonal separation for each pair of diagonal is allowed to vary together ensuring half symmetry of the structure at all times. The optimization is run under a uniaxial loading condition. The color of each point on the graph corresponds to the optimum value of mass ratio for that particular number of diagonals. Four deformation plots of the optimum structure and buckling modes are provided on the right for their respective number of diagonals.}
    \label{BucklingOptimization}
\end{figure}

@@

\section{Local and Global Instabilities}
\mf{How should I go about describing this here?}
\begin{figure}
	\centering
	\includegraphics[width=0.7\linewidth]{SFig12.pdf}
	\caption{{\bf Schematic depicting parameters of Optimization.} This schematic shows an example optimization geometry  at a complexity level of five diagonals. For each set of even diagonals, we allow each diagonal to travel away from each other from the center junction with distances $S_1,S_2$. Note that for every odd diagonal, the distance $S_0=0$ and it is not allowed to vary in order to ensure symmetry.}
	\label{DomainSizeSchematic}
\end{figure}
% Bibliography
%\nocite{aizenberg2005}
%\nocite{deshpande2001}
%\nocite{miserez2008}
%\nocite{weaver2010}

>>>>

For all buckling analysis, we performed a linear stability buckling analysis ({\tt *Buckling} command in ABAQUS input file). We perform this analysis for varying angles $\theta$ and extract the first mode critical buckling strain. Since buckling may alter the periodicity of the
structure, we considered super cells consisting of $M \times M$
undeformed RVEs subjected to periodic boundary
conditions and calculated the critical strain for each of
them. The critical strain of the infinite periodic structure is
then defined as the minimum critical strain on all considered
super cells. See \cref{DomainSize} for this detailed analysis.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{SFig6.pdf}
    \caption{{\bf Buckling Optimization.} Graph shows optimal value of critical buckling strain for varying number of diagonals. For all simulations, the total mass of the structure is maintained constant while the mass-ratio is allowed to vary. Furthermore, the diagonal separation for each pair of diagonal is allowed to vary together ensuring half symmetry of the structure at all times. The optimization is run under a uniaxial loading condition. The color of each point on the graph corresponds to the optimum value of mass ratio for that particular number of diagonals. Four deformation plots of the optimum structure and buckling modes are provided on the right for their respective number of diagonals.}
    \label{BucklingOptimization}
\end{figure}

@@

\section{Local and Global Instabilities}
\mf{How should I go about describing this here?}
\begin{figure}
	\centering
	\includegraphics[width=0.7\linewidth]{SFig12.pdf}
	\caption{{\bf Global vs Local Instabilities.} This figure shows four identical analysis performed on the Designs A-D. For each analysis we obtain the critical buckling strain for varying $M\times M$ tessellations (y-axis) of the unit cell also for varying loading angle $\theta$ (x-axis). The color of a pixel corresponds to a value of critical buckling strain for that simulation. For each of the simulations, periodic boundary conditions are applied along the outer perimeter of the $M\times M$ structure. This plot conveys that for Designs A-C the prominent buckling mode is the local mode, whereas for Design D, the prominent mode is a global mode. Choosing a sufficiently large $M$ allows Design D to converge to a finite value for each $\theta$.}
	\label{DomainSize}
\end{figure}
% Bibliography
%\nocite{aizenberg2005}
%\nocite{deshpande2001}
%\nocite{miserez2008}
%\nocite{weaver2010}
